\subsection{Bounded Sets and Balls}

\begin{majorEx}%4.F
    Prove that a set $A$ is bounded iff $A$ is contained in a ball.
\end{majorEx}

\begin{proof}
  We will first show that if a set $A$ is bounded then it is contained
  in a ball. Because $A$ is bounded, we know that there is a number
  $d>0$ such that for any $x,y \in A$, that $\rho(x,y)<d$. We thus
  have that for an arbitrary point $a$ that $B_d(a)$ will contain
  every point in $A$, by the definition of a ball.

  We will now show that if a set $A$ is contained in a ball, that it
  is bounded. Let $B_r(a)$ be a ball which contains $A$. Let $x,y\in
  A$ be arbitrary. We see that by the triangle inequality, that 
  $\rho(x,y)\leq \rho(x,a) + \rho(y,a)$, and by the definition of a
  ball, we have that $\rho(x,a)<r$, and  $\rho(y,a)<r$ as $A$ is
  contained within the ball. We thus would see that  $\rho(x,y)< 2r$,
  and thus as $x,y\in A$ were arbitrary, that  for any $x,y$, we have
  that $\rho(x,y)< 2r$, and as $2r>0$, we know that $A$ is bounded by
  the definition of bounded.
\end{proof}
Primary Author: Reilly Noonan Grant

\begin{minorEx}%4.14
    What is the relation between the minimal radius of such a ball and
    $\mathrm{diam}(A)$?
\end{minorEx}

\begin{proof}[Answer]
  $2r\geq \mathrm{diam}(A) \geq r$, where $r$ is the minimal radius of such a
  ball. We see that $2r\geq \mathrm{diam}(A)$ above, as for an
  arbitrary ball with radius $r$, for any $x,y\in A$,
  $\rho(x,y)<2r$. We will now show that $\mathrm{diam}(A) \geq r$.
  We will show this using proof by contradiction. We assume for
  sake of contradiction, that  $\mathrm{diam}(A) < r$. Let a ball
  which contains $A$ be $B_r(a)$. We would then have that for any $x\in B_r(a)$
  have that $\rho(a,x)<\mathrm{diam}(A)<r$, and thus $r$ is not the
  minimal radius, and we have a contradiction. 
  We thus have that $2r\geq \mathrm{diam}(A) \geq r$.
\end{proof}
Primary Author: Reilly Noonan Grant
