\subsection{Segments (What Is Between)}

\begin{minorEx}%4.12
    Prove that the segment with endpoints $a,b \in \RR^n$ can be described as 
    \[
        \set{x \in \RR^n : \rho(a,x) + \rho(x,b) = \rho(a, b)},
    \]
    where $\rho$ is the Euclidean metric.
\end{minorEx}

\begin{proof}
  Let $a,b \in \RR^n$ be arbitrary, and let them define a segment. Let
  $c$ be an arbitrary point on that segment. We see that the distance
  between $c$ and $a$ is given by $\rho(a,c)$, and the distance
  between $c$ and $b$ is given by $\rho(c,b)$. We also see that as $c$
  is on the segment, that the shortest distance between $a$ and $b$,
  given by $\rho(a,b)$, can also be given by moving from $a$ to $c$,
  and then from $c$ to $b$. We see that the distance given from moving
  from $a$ to $c$, and then $c$ to $b$ is also given by
  $\rho(a,c)+\rho(c,b)$, and thus $\rho(a,c)+\rho(c,b)= \rho(a,b)$. We
  thus have that if $c$ is on the segment, that $\rho(a,c)+\rho(c,b)=
  \rho(a,b)$. We can also see that if we know that $\rho(a,c)+\rho(c,b)=
  \rho(a,b)$, that we know that going from $a$ to $c$, and then $c$ to
  $b$ is the shortest distance between $a$ to $b$, and thus $c$ is on
  the segment between $a$ and $b$. As $c$ was arbitrary, and we showed
  both that $\rho(a,c)+\rho(c,b)= \rho(a,b)$ implies $c$ is on the
  segment, and that $c$ being on the segment implies that
  $\rho(a,c)+\rho(c,b)= \rho(a,b)$, we know the 
  segment with endpoints $a,b \in \RR^n$ can be described as 
    \[
        \set{x \in \RR^n : \rho(a,x) + \rho(x,b) = \rho(a, b)},
    \]
    where $\rho$ is the Euclidean metric.
\end{proof}

Primary Author: Reilly Noonan Grant

\begin{minorEx}%4.13
    How does the set defined as in Problem 4.12 look if $\rho$ is the metric
    defined in Problems 4.1 or 4.2? (Consider the case where $n = 2$ if it seems
    to be easier.)
\end{minorEx}

\begin{proof}[Answer]
  We first consider the set defined in Problem 4.12 using the metric
  defined in problem 4.2. We see that this metric can be thought to
  measure the distance from one point to the next by traveling only 
  on the axes. We thus would see that the set would be a rectangle
  defined with the corner points being the points $a,b$ in the
  segment. We also see that this generalizes from $\RR^2$ to $\RR^3$,
  defining a rectangular box, and similarly generalizes into higher
  dimensions.

  We now consider the set using the metric defined in problem 4.1. We
  see that this metric is the set of all points $c$, where the biggest
  difference in the components of $a$ and $b$ is equal to the biggest
  difference in the components $a$ and $c$ plus the biggest difference in the
  components of $c$ and $b$. We see that this seems to form a dimond
  like shape in $\RR^2$ and $\RR^n$ in cases where the points do not
  define a box. When the points define a box, a segment is identical
  to a segment with the standard topology of $\RR^n$.
\end{proof}

Primary Author: Reilly Noonan Grant