\subsection{Cantor Set}

\begin{majorEx}
    Find a geometric description of $K$.

    Prove that
    \begin{enumerate}
        \item $K$ is contained in $[0,1]$,
        \item $K$ does not meet $(\frac{1}{3}, \frac{2}{3})$,
        \item $K$ does not meet $\left( \frac{3s+1}{3^k}, \frac{3s+2}{3^k}
            \right)$ for any integers $k$ and $s$.
    \end{enumerate}

    Present $K$ as $[0,1]$ with an infinite family of open intervals removed.

    Try to sketch $K$.
\end{majorEx}

\begin{proof}
    To see that $K \subseteq [0,1]$, we argue that $\min(K) = 0$ and $\max(K) =
    1$. Let $\set{a_k}_{k=1}^{\infty}$ be a sequence defined such that $a_k \in
    \set{0,2}$ for all $k$. We have 
    \[
        0 \leq a_k \leq 2,
    \]
    so it follows that
    \[
        \sum_{k=1}^{\infty} \frac{0}{3^k} \leq
        \sum_{k=1}^{\infty} \frac{a_k}{3^k} \leq
        \sum_{k=1}^{\infty} \frac{2}{3^k}.
    \]
    The left side simplifies to $0$, and for the right side, noting that
    \[
        \sum_{k=0}^{\infty} \frac{1}{3^k} = \frac{1}{1-\frac{1}{3}} =
        \frac{3}{2},
    \]
    we have 
    \[
        \sum_{k=1}^{\infty} \frac{2}{3^k} = 2 \cdot \left( \frac{3}{2} -
        1\right) = 1.        
    \]
    Hence, for all $\set{a_k}_{k=1}^{\infty}$ properly defined, we have 
    \[
        0 \leq \sum_{k=1}^{\infty} \frac{a_k}{3^k} \leq 2.
    \]

    To see that $(\frac{1}{3}, \frac{2}{3}) \not \subseteq K$, suppose
    $\set{a_k}_{k=1}^{\infty}$ is such that $a_1 = 0$ and $a_k = 2$ for all $k >
    1$. Then
    \begin{align*}
        \sum_{k=1}^{\infty} \frac{a_k}{3^k} &= 0 + 2\sum_{k=2}^{\infty}
        \frac{1}{3^k} \\
        &= 2\sum_{k=0}^{\infty} \frac{1}{3^k} - 2 - \frac{2}{3} \\
        &= 3 - 2  - \frac{2}{3} \\
        &= \frac{1}{3}.
    \end{align*}
    Now suppose that $\set{a_k}_{k=1}^{\infty}$ is such that $a_1 = 2$ and $a_k
    = 0$ for all $k > 1$. Then
    \[
        \sum_{k=1}^{\infty} \frac{a_k}{3^k} = \frac{2}{3} + \sum_{k=2}^{\infty}
        \frac{0}{3^k} = \frac{2}{3}.
    \]
    This shows that, even given the value of $a_1$, no sequence
    $\set{a_k}_{k=1}^{\infty}$ generates a series value in
    $(\frac{1}{3}, \frac{2}{3})$.

    Assume that after $k$ terms the sequence $\set{a_n}$ is either all 0s or all
    2s. For a given $(\frac{3s+1}{3^k}, \frac{3s+2}{3^k})$, the upper bound is
    achieved with trailing 0s, and the lower bound is achieved with trailing 1s.
    Permutations of 0s and 2s in the first $k$ elements bounds the sequence
    around a given third.

    We may write $K$ as 
    \[
        K = [0,1] \setminus \bigcap_{k, s \in \NN} \left((\frac{3s+1}{3^k},
        \frac{3s+2}{3^k})\right).
    \]
\end{proof}

Primary author: David Kraemer

\begin{majorEx}
Prove that $K$ is a closed set in the real line.
\end{majorEx}

\begin{proof}
We will take the complement of the Cantor set $(\{\Sigma_{k=1}^\infty a_k/3^k | a_k \in {0, 2}\})^c$ and label it $C^c$. In the construction of the
Cantor set, we know that $(\{\Sigma_{k=1}^n a_k/3^k | a_k \in {0, 2}\})^c$ $(n \in \RR)$ is a open set, and the addition of $(\{\Sigma_{k=1}^{n+1} a_k/3^k | a_k \in {0, 2}\})^c$ which is also open, is the intersection of two open sets, and will still result in a open set. Thus., $(\{\Sigma_{k=1}^\infty a_k/3^k | a_k \in {0, 2}\})^c$ is a intersection of open sets, and it is still a open set. By definition $\{\Sigma_{k=1}^\infty a_k/3^k | a_k \in {0, 2}\}$ which is the Cantor Set, is closed.
\end{proof}

